---
title: "Introduction to StatComp21093"
author: 'Zhang Shan'
date: "2021/12/18"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp21093}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp21093__ is a simple R package developed to estimate the parameter of the two-component Gaussian mixture distribution with EM algorithm and the Gibbs sampling for the mixed distribution. Two functions are considered, namely, _EM_mix_ (EM Algorithm for two-component Gaussian mixture) and _Gibbs_mix_ (Gibbs sampling for two-component Gaussian mixture).

In the EM_mix, we estimate the $\mu_1,\mu_2,\sigma_1^2,\sigma_2^2,p$ with the EM algorithm;

The source R code for _EM_mix_ is as follows:
```{r}
EM_mix<-function(mu1,sigma1,mu2,sigma2,p,N,rv){
  phi<-rep(0,N)
  for (i in 1:1000) {
    #E-step
    for (j in 1:N) {
      f1<-dnorm(rv[j],mu1,sigma1)
      f2<-dnorm(rv[j],mu2,sigma2)
      phi[j]<-p*f2/((1-p)*f1+p*f2)
    }
    #M-step
    mu1<-sum((1-phi)*rv)/sum(1-phi)
    s1<-sum((1-phi)*(rv-mu1)^2)
    mu2<-sum(phi*rv)/sum(phi)
    s2<-sum(phi*(rv-mu2)^2)/sum(phi)
    sigma1<-sqrt(s1)
    sigma2<-sqrt(s2)
    p<-sum(phi)/N
  }
  return(c(mu1,sigma1,mu2,sigma2,p))
}
rv_mix<-function(N,p){
  u1<-rnorm(N,0,1)
  u2<-rnorm(N,2,1)
  j<-runif(N)
  k<-as.integer(j>p)
  u<-k*u1+(1-k)*u2
  return (u)
}
```

In the Gibbs_mix, for simplicity we fix the $\sigma_1^2,\sigma_2^2$ and mixing proportion $p$ at their maximum likelihood values (with the above EM algorithm) so that the only unknown parameters are the mwans $\mu_1$ and $\mu_2$.

The source R code for _Gibbs_mix_ is as follows:
```{r}
Gibbs_mix<-function(mu1,mu2,sigma1,sigma2,p,N,rv){
  X<-matrix(0,1000,2)
  z<-rep(0,N)
  for (i in 1:1000) {
    for (j in 1:N){
      f1<-dnorm(rv[j],mu1,sigma1)
      f2<-dnorm(rv[j],mu2,sigma2)
      phi<-p*f2/((1-p)*f1+p*f2)
      
      u<-runif(1)
      if(u<phi){
        z[j]<-1
      }else{
        z[j]<-0
      }
    }
    mu1<-sum((1-z)*rv)/sum(1-z)
    mu2<-sum(z*rv)/sum(z)
    X[i,1]<-rnorm(1,mu1,sigma1)
    X[i,2]<-rnorm(1,mu2,sigma2)
  }
  return(X)
}
rv_mix<-function(N,p){
  u1<-rnorm(N,0,1)
  u2<-rnorm(N,2,1)
  j<-runif(N)
  k<-as.integer(j>p)
  u<-k*u1+(1-k)*u2
  return (u)
}
```


